Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-21 ms/manuscript.Rmd
Change fig with from 7 to 7.25 in

```{r raw-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("raw-diversity"), "pdf"), width = 7, height = 4, units = "in", raw_diversity_plot)
```

```{r raw-diversity-print, fig.width = 7, fig.height = 4, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
raw_diversity_plot
```

@@

```{r rand-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("rand-diversity"), "pdf"), rand_diversity_plot, width = 7, height = 8, units = "in")
```

```{r rand-diversity-print, fig.width = 7, fig.height = 9, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
rand_diversity_plot
```

@@

```{r coeff-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("coeff"), "pdf"), coeff_plot, width = 7, height = 5, units = "in")
```

```{r coeff-print, fig.width = 7, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
coeff_plot
```

@@

```{r modelfit-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("modelfit"), "pdf"), modelfit_plot, width = 7, height = 5, units = "in")
```

```{r modelfit-print, fig.width = 7, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
modelfit_plot
```

@@

```{r bioregions-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("bioregions"), "pdf"), bioregions_plot, width = 7, height = 5, units = "in")
```

```{r bioregions-print, fig.width = 7, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
bioregions_plot
```

@@

```{r div-by-tax-region-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("div-by-tax-region"), "pdf"), div_by_tax_region_plot, width = 7, height = 7, units = "in")
```

```{r div-by-tax-region-print, fig.width = 7, fig.height = 7, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
div_by_tax_region_plot
```

@@

```{r conserv-status-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("conserv-status"), "pdf"), conserv_status_plot, width = 7, height = 4, units = "in")
```

```{r conserv-status-print, fig.width = 7, fig.height = 4, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
conserv_status_plot
```

>>>>

```{r raw-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("raw-diversity"), "pdf"), width = 7.25, height = 4, units = "in", raw_diversity_plot)
```

```{r raw-diversity-print, fig.width = 7.25, fig.height = 4, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
raw_diversity_plot
```

@@

```{r rand-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("rand-diversity"), "pdf"), rand_diversity_plot, width = 7.25, height = 8, units = "in")
```

```{r rand-diversity-print, fig.width = 7.25, fig.height = 9, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
rand_diversity_plot
```

@@

```{r coeff-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("coeff"), "pdf"), coeff_plot, width = 7.25, height = 5, units = "in")
```

```{r coeff-print, fig.width = 7.25, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
coeff_plot
```

@@

```{r modelfit-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("modelfit"), "pdf"), modelfit_plot, width = 7.25, height = 5, units = "in")
```

```{r modelfit-print, fig.width = 7.25, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
modelfit_plot
```

@@

```{r bioregions-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("bioregions"), "pdf"), bioregions_plot, width = 7.25, height = 5, units = "in")
```

```{r bioregions-print, fig.width = 7.25, fig.height = 5, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
bioregions_plot
```

@@

```{r div-by-tax-region-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("div-by-tax-region"), "pdf"), div_by_tax_region_plot, width = 7.25, height = 7, units = "in")
```

```{r div-by-tax-region-print, fig.width = 7.25, fig.height = 7, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
div_by_tax_region_plot
```

@@

```{r conserv-status-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(result_file(figure("conserv-status"), "pdf"), conserv_status_plot, width = 7.25, height = 4, units = "in")
```

```{r conserv-status-print, fig.width = 7.25, fig.height = 4, eval = params$doc_type == "pdf"}
# Print plot if rendering to PDF
conserv_status_plot
```
